Regression Cube Analysis of Cohort Study Data

### 2015-03-19 draft.tex
revised version from Bernhard and Sylvia

%% If you are submitting a paper to a conference for review with a double
%% blind reviewing process, please replace the value ``0'' below with your
%% OnlineID. Otherwise, you may safely leave it at ``0''.
%% TODO: Blind Review: Replace with online ID
\onlineid{0}

@@

%% Abstract section.
\abstract{%
\com{Problem}.
Epidemiological studies comprise heterogeneous data about a subject group (a \emph{cohort}) to define disease-specific risk factors.
%%
These data contain information (\emph{features}) about a subjects' lifestyle, medical conditions and also medical images of the whole body.
%%
These features are analyzed using statistical regression analyses towards features indicating a disease (the \emph{target feature}).
%%
Overview visualizations over a whole data sets towards a target feature are highly required, but not available to epidemiologists.
%%
%These analyses usually include two to five features (\emph{independent features}) towards the investigated condition.
\com{New Solution}.
%(New Solution).

We propose a new analyses approach of epidemiological data sets by incorporating all features in an exhaustive regression-based analysis.
%%
This approach combines all \emph{independent features} towards a \emph{target feature} and provides a visualization, which allows for insights into the data by highlighting relationships. %showing the
%%
A 3D-visualization of all combinations of two to three independent features towards a target acts as an overview over the whole data set, the \emph{Regression Cube}.
%%
%We call it the \emph{Regression Cube}.
%%
Slicing through the \emph{Regression Cube} allows for the detailed analysis of features towards the target disease.
%%
The regression model can be adjusted by the user to describe disease-specific hypotheses.
%%
Furthermore, the influences of features can be assessed using a difference view, comparing different calculation results.
\com{Validation}.
%%
We applied our \emph{Regression Cube} method to a hepatic steatosis data set to reproduce results from a data-mining driven analysis.
%%
We conducted a qualitative analysis with three domain experts on a breast fat data set to derive insights into the correlation between breast lesions and non-image variables.
%%
\com{Results}.
%%
With our technique we were able to reproduce results from a data mining analysis of a hepatic steatosis data set.
%%
By applying it to a breast fat data set we were able to derive new hypotheses about relations between breast fat density and breast lesions towards breast cancer.
%%
\com{Implications}.
Epidemiological data sets can for the first time be visually overviewed using a regression-based analysis of all features towards a disease. 
%With our technique it is possible for the first time to provide a overview visualization of variables regarding a target variable.

} % end of abstract

>>>>

%% If you are submitting a paper to a conference for review with a double
%% blind reviewing process, please replace the value ``0'' below with your
%% OnlineID. Otherwise, you may safely leave it at ``0''.
%% TODO: Blind Review: Replace with online ID
\onlineid{175}

@@

%% Abstract section.
\abstract{%
\com{Problem}.
Epidemiological studies comprise heterogeneous data about a subject group (a \emph{cohort}) to define disease-specific risk factors.
%%
These data contain information (\emph{features}) about a subjects' lifestyle, medical conditions and also medical image data.
%%
These features are analyzed using statistical regression analysis to identify feature combinations indicating a disease (the \emph{target feature}).
%%
Although there is a strong demand for overview visualizations of a whole data set towards a target feature, no suitable tool is available for epidemiological researchers.

\com{New Solution}.
%%
We propose an analysis approach of epidemiological data sets by incorporating all features in an exhaustive regression-based analysis.
%%
This approach combines all \emph{independent features} with respect to a \emph{target feature} and provides a visualization, which reveals insight into the data by highlighting relationships.
%%
A 3D-visualization of all combinations of two to three independent features towards a target acts as an overview of the whole data set, the \emph{Regression Cube}.
%%
Slicing through the \emph{Regression Cube} allows for the detailed analysis of features towards the target disease.
%%
Expert knowledge about disease-specific hypotheses can be included into the analysis by adjusting the regression model formulas.
%%
Furthermore, the influences of features can be assessed using a difference view comparing different calculation results.
%%
\com{Validation \& Results}.
%%
We applied our \emph{Regression Cube} method to a hepatic steatosis data set to reproduce results from a data-mining driven analysis.
%%
A qualitative analysis with three domain experts was conducted on a breast fat data set.
%%
We were able to derive new hypotheses about relations between breast fat density and breast lesions towards breast cancer.
%%
\com{Implications}.
%%
With our work, we present a visual overview of epidemiological data with the \emph{Regression Cube}, which allows for the first time a interactive regression-based analysis of large feature sets with respect to a disease.
} % end of abstract
